\iffalse
STRUCTUR and notes from Iddo:
6-8 pages
Abstract
Introduction
    related work
Methods
    architecture
Results
    implementation
References

Make sure to answer the following:
What is your report about
    Talk about realated work where similar techniques and experiments have been used but applied to a different problem
Why should anyone care about this
    What problem does it solve
    Why is the problem interesting
What is really new and why is it neat
    State what are other solutions to the problem, and why they are not satisfactory
    Explain your solution, say why it is better
    State the limitations of results

Figures and captions - should be self contained (stand on their own)
Use active voice

Questions for reviewers:
1. Briefly summarize the project.
2. What are a few strengths of the project?
3. What are potential weaknesses of the project?
4. Does the report consider previous approaches or is there major work which is missing?
5. Is the problem clearly stated? Does it make sense?
6. Is the method clearly described? If not, which paragraphs or statements are unclear.
7. Is there a new or useful component to the project?
8. Is there a repository with data, models, code? Is the code documented?
\fi

\iffalse
THINGS WE SHOULD FIND ANSWERS FOR:
Why can't all collaborators just use the same 5M GEMC events?
---- I think the answer is that having standard background files could introduce systemic bias into results? If there isn't a stronger answer here, we may need to change focus of project
Why is it that we can't just sample directly from the "distributions" produced by 5M x data points?
 --- I think the answer is that there isn't a formal way to do so, since all we have is samples from some unknown distribution
 Why is our loss negative?
\fi

\iffalse
\section{To Do}

Problem with doubles - slows down computation by a lot

Need to rewrite motivation to include the fact that we will not improve precision by generating events from the model, and instead need to use e.g. allow 50 collaborators to pull 10M events from a trained generator,

Rewrite method to include UMNN and motivation for it [\citet{wehenkel2019unconstrained})]

Rewrite introduction to include stuff from ICLR, Jesse Thaler stuff

Enfore energ;y and momentum conservation

Difference between 1 feature training, 2, 4, and 16

Investagat G1 energy issue


Note that MAF is fast to train but slow to sample from
\fi